### 2023-04-04 chapter2/chapter2.tex
Added method section for alignments and trees

\subsection{Alignment and tree generation}

>>>>

\subsection{Alignment and tree generation}
Alignments of single copy orthologs and the outputs of the missing data phylo-HMM were obtained from the analyses conducted in chapter~\ref{chapter:1}. Likewise, we used the LG consensus tree generated by the ``non-invariant, 100\% redundancy'' sampling strategy as the input or reference where indicated in subsequent phylogenetic analyses.
